---
title: "Binomial Package Introduction"
author: "Hika Masuda"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binomial Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set( collapse = TRUE, comment = "#>")
library(binomial)
```

##Introduction
This package "binomial" allows the user to create a binomial distribution under a constant probability, with a fixed number of trials. It also allows the user to visualize such distributions through plotting functions.

#Usage
##bin_choose()
This is the basic choose function, which gives the number of combinations possible when choosing k items from n items.

Some examples of how to implement bin_choose():
```{r}
bin_choose(n = 5, k = 2)
bin_choose(n = 8, k = 5)
```

##bin_probability()
This is the basic binomial probability function, which gives the probability that one gets the given number of successes in the given number of trials, assuming a costant probability.

Some examples of how to implement bin_choose():
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
#success can also be a vector, as long as it is less than equal to the number of trials
bin_probability(success = 1:3, trials = 5, prob = 0.3)
```

##bin_distribution()
This function allows you to create a binomial probability distribution given the number of trials and a fixed probability. This object has class "bindis". By calling plot(), you can also visualize this binomial distribution as a bar graph.

Here is an example of what this looks like:
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

##bin_cumulative()
This function allows you to not only find the binomial distribution given the number of trials and fixed probability, but also the cumulative probability at each number of successes. The cumulative probability is the probability of a certain number of successes added with the probability of successes fewer than the original number. The object returned has class "bincum". You can also plot the cumulative distribution using plot.

Here is an example of what this looks like:
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
plot(dis2)
```

##bin_variable()
This function allows you to create a binomial variable with class "binvar". It will return a list with the number of trials and probability given, and will output a description of the variable.
By calling summary on this "binvar" object, you will be able to see the summary statistics for the binomial variable such as mean, mode, and skewness.

Here is an example of what this looks like:
```{r}
bin1 <- bin_variable(trials = 5, prob = 0.5)
binsum1 <- summary(bin1)
binsum1
```

## Functions of measures
If you want to calculate individual measures without having to create a binomial variable and using summary, you can use the following functions of measures to do so.

```{r}
bin_mean(10, 0.3) #calculates mean
bin_variance(10, 0.3) #calculates variance
bin_mode(10, 0.3) #calculates mode
bin_skewness(10, 0.3) #calculates skewness
bin_kurtosis(10, 0.3) #calculates kurtosis
```
